\documentclass{report}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue,bookmarksopen=true]{hyperref}
\usepackage{bookmark}
\input{../physics_common}

\title{Playbook of Equity Trading}
\author{Xie Xiaolei}
\date{\today}

\begin{document}
\maketitle

\chapter{Order Execution}
\section{Order Types}
\begin{enumerate}
\item Market order - executed immdiately at the best available price from the order book.
  Different prices for different batches of the same order may be the result for large-volume orders.
  
\item Limit order - may or may not be executed. Must be set at a lower price than the market price
  for buy limit orders and at a price higher than the market price for sell limit orders.
  The executed price is the limit price or better.

  Conditions can be attached to a limit order:
  \begin{itemize}
  \item {\it fill-or-kill (FOK)}: The order must be executed immediately and completely or otherwise
    cancelled altogether.
  \item {\it all-or-none (AON)}: The order need not be executed immediately - a later time is OK - but it must
    be executed at its entirety. For a buy order, the order book must have enough shares on offer at prices equal to
    or lower than the limit price for the order to be carried through.
    Conversely, for a sell order, the order book must have enough bids at prices equal to or higher than the limit price.
  \end{itemize}

  Validity in time of an order can also be specified:
  \begin{itemize}
  \item {\it Good-till-canceled}: Valid until canceled.
  \item Valid until a specified time point, e.g. the end of the trading day.
  \end{itemize}

\item Stop order - think of stop loss.
  For a sell stop order, the order is triggered as soon as a transaction is observed at
  a price equal to or lower than the stop price; the order then becomes a market order.
  For a buy stop order, the order is triggered as soon as a transaction is observed at
  a price equal to or higher than the stop price.
  
\item Stop-limit order - similar to a stop order, but is converted to a limit order when triggered.

\end{enumerate}

\section{Execution Algorithms}
\begin{enumerate}
\item {\bf Volume Weighted Average Price}

  ``However, there are other uses for the VWAP, and one such strategy is to purchase a stock for individual investors just as the VWAP pierces the intraday VWAP moving average, as this can indicate a momentum shift in the share price.''- Investpedia

  ``Often, a VWAP trade will buy or sell 40\% of a trade in the first half of the day and then the other 60\% in the second half of the day''.    - Wikipedia
  
\item{\bf Time Weighted Average Price}

``A TWAP trade would most likely execute an even 50/50 volume in the first and second half of the day'' - Wikipedia

  
\end{enumerate}

\input{MarketImpact}
\input{TradingStrategy}

\bibliographystyle{unsrt}
\bibliography{../../../kkasi/thesis/econophysics}
\end{document}
